%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Machine Learning Cloud Platform Architect} % Job title
    {SmartMore Inc.} % Organization
    {Beijing, China} % Location
    {Apr. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {China Computing NET: Computing Power Scheduling Platform: Implemented a multi-cluster heterogeneous scheduler based on the Karmada scheduling framework. This includes the management of Kubernetes container platforms, supercomputing platforms, and OpenStack platforms. Supported multi-cluster scheduling strategies include priority scheduling, fair scheduling, algorithmic-based scheduling, affinity scheduling, and rescheduling.}
        \item {cubeml Machine Learning Platform: Involved in the architecture and core functionality development of the CubeML machine learning platform. Implemented the CubeML machine learning platform based on the Volcano batch scheduling system, covering the development of scheduling, AI container, distributed development and training, inference services, etc. Also addressed and resolved preemption scheduling issues in Volcano open source project.}
        \item {Hyper-Converged System: Engaged in the architecture design and development of the Hyper Converged system. Main responsibilities include system architecture design and technology selection; leading the research, development, and implementation of distributed training, container development, and large-scale model training.}
        \item {Machine Learning Platform Implementation Projects: Projects include the Peng Cheng Laboratory multi-cluster Scheduling, Shanghai University Machine Learning Platform, Tongji University Machine Learning Platform, Chengdu Internet Machine Learning Platform, and more.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Cloud Platform Development Engineer} % Job title
    {Kingsoft Cloud Inc.} % Organization
    {Beijing, China} % Location
    {Mar. 2020 - Apr. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {KingAI Machine Learning Platform: Research and Development of the AI Container Development Module. This module primarily includes SSH login, integration and authentication of Jupyter notebooks, and distributed development and training. It seamlessly integrates with the entire KingAI platform, providing an all-in-one machine learning development experience.}
        \item {KingAI Machine Learning Platform: Inference Service Development. Redesigned and restructured the inference service module, overhauled online inference, significantly streamlined the number of online inference services, and improved the stability of the inference services.}
        \item {KingAI Machine Learning Platform: Fine-grained Authentication for Services, Service Traffic Governance, and more.}
      \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Student} % Job title
    {The Institute of Computing Technology, Chinese Academy of Sciences (ICT)} % Organization
    {Beijing, China} % Location
    {Jul. 2017 - Apr. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Public Opinion Monitoring System: Refactoring and developing a new version of the distributed service framework for keyword analysis, sentiment analysis, named entity recognition, segmentation, text classification, news extraction, etc. Through a plugin mechanism, a revamped framework is created to significantly enhance service scalability.}
        \item {Machine Learning Experiment Platform: Set up a continuous integration Jenkins + Harbor + Kubernetes cluster to achieve continuous integration and delivery of services, accelerating delivery. Automated the laboratory process from code development to deployment testing environment, enhancing development efficiency.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Android Software Engineer} % Job title
    {Beijing Certificate Authority Co., Ltd (BJCA)} % Organization
    {Beijing, China} % Location
    {Jul. 2015 - Jul. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Product Development: Responsible for defining and developing requirements for the Android SDK of the Xinshou Shu product.}
        \item {Project Customization: Customized development for projects such as China Life and Shanghai Bank.}
        \item {Project Implementation: Responsible for providing technical support for project implementation using SDKs.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
